Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-16 paper/paperv3.qmd
comparison to linear for h3

@@

str_glue("
pi1a: {round(pi1a, 5)}
pi2a: {round(pi2a, 5)}
pi1b: {round(pi1b, 5)}
pi2b: {round(pi2b, 5)}")

str_glue("
delta pi a {round(100 * (pi1a - pi2a) / pi2a, 2)}%,
delta pi b {round(100 * (pi1b - pi2b) / pi2b, 2)}%")
```

>>>>

### H3: Offspring Sex Ratio

```{r}
#| label: linear-h3

#h2a
sexrat_line <- glmer(
  is_male ~ age10 + (1 | animalID) + (1 | year),
  pup_sex_data, 
  family = "binomial",
  control = glmerControl(optimizer = "bobyqa")
)

summary(sexrat_line)$coefficients

```{r}
#| label: quad-h3

sexrat_quad <- glmer(
  is_male ~ poly(age10, 2, raw = TRUE) + (1 | animalID) + (1 | year_fct),
  pup_sex_data,
  family = "binomial",
  control = glmerControl(optimizer = "bobyqa")
)

h3_age10_peak <- -summary(sexrat_quad)$coefficients[2, 1] / 
  (2 * summary(sexrat_quad)$coefficients[3, 1])
h3_age_peak <- h3_age10_peak * 10 + age_senesce

sprintf("Age peak (H2a) = %0.1f", h2a_age_peak)
```

@@

str_glue("
P1: {round(pi1a, 5)}
P2: {round(pi2a, 5)}
M1: {round(pi1b, 5)}
M2: {round(pi2b, 5)}")

str_glue("
delta P {round(100 * (pi1a - pi2a) / pi2a, 2)}%,
delta M {round(100 * (pi1b - pi2b) / pi2b, 2)}%")
```
